data_collation

### 2024-05-23 scripts/data_cleaning.Rmd
updated fish data

# Combine rugosity dataframes
```{r}

>>>>

# Combine rugosity dataframes
```{r}
# add a YEAR column for 2021 data
# Add a new column named "year" with all values set to 2021
rugosity_2021_DEM <- data.frame(YEAR = 2021, rugosity_2021_DEM)

# use rbind.fill() method in R to combine data frames with different columns
rug_data <- rbind.fill(rugosity_2019_DEM, rugosity_2020_DEM, rugosity_2021_DEM)

#remove 22-25 columns for observers not needed information
rug_data <- rug_data[ -c(22:25) ]

# Rename Kings Beach to King's Beach
rug_data$SITE[rug_data$SITE == "Kings Beach"] <- "King's Beach"
rug_data$SITE[rug_data$SITE == "KB"] <- "King's Beach"

# rename rugosity data columns
rug_data <- rug_data %>%
  rename(
    "0M" = "X0M",
    "4M" = "X4M",
    "8M" = "X8M",
    "12M" = "X12M",
    "16M" = "X16M",
    "20M" = "X20M",
    "24M" = "X24M",
    "28M" = "X28M",
    "32M" = "X32M",
    "36M" = "X36M",
    "40M" = "X40M", 
    "DEPTH.0M" = "DEPTH...0M..ft.",
    "DEPTH.40M" = "DEPTH....40M.",
    "VIS.M" = "VIS..M."
    )

# output updated dataframe
write.csv(rug_data, "output/cleaned_data/rugosity.data.clean.csv", row.names = FALSE)
